\speculake: Hiding Malware in Speculative Execution

### 2018-05-09 paper/figures.tex
specify iterations in bandwidth figure

\newcommand{\FigSpecBandwidth}{
\begin{figure}[t]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/Speculative_bandwidth}
    \caption{Speculative Bandwidth---Using the speculative primitive 
        1KB of data can be decrypted and exfiltrated at a speed between 5 and 6 kbps
        from the speculative world. Varying the width of the channel 
        results in competing performance factors -- decreasing the 
        number of loops vs decreased size of the probe space.}
    \label{fig:spec_bandwidth}
\end{figure}
}

>>>>

\newcommand{\FigSpecBandwidth}{
\begin{figure}[t]
    \centering
        \includegraphics[width=0.5\textwidth]{figures/Speculative_bandwidth}
    \caption{Speculative Bandwidth---Using the speculative primitive 
        1KB of data can be decrypted and exfiltrated at a speed between 5 and 6 kbps
        from the speculative world with 20 iterations per
        round for guaranteed correctness.  Varying the width of the channel 
        results in competing performance factors -- decreasing the 
        number of loops vs decreased size of the probe space.}
    \label{fig:spec_bandwidth}
\end{figure}
}
